Spike-and-Slab Generalized Additive Models and Scalable Algorithms for High-Dimensional Data

### 2022-02-18 Manuscript/03-Simulation.Rmd
Add bi-level selection section

<!-- %are calculated to assess out-of-sample estimation accuracy, -->

>>>>

\bg{\subsubsection{Bi-level Selection}
Among the methods of comparison, there are two methods is possible for bi-level selection, i.e. the proposed BHAM and spikeSlabGAM. Hence, in this section, we further investigate the bi-level selection of the proposed models. } 
<!-- %are calculated to assess out-of-sample estimation accuracy, -->
